NTM CT Scoring - Initial Agreement

### 2022-11-28 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
added kappas

# Fleiss' Kappa by Feature

```{r}

```

>>>>

# Agreement by Feature

## Atelectasis

```{r}
feat = "Atelectasis"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Bronchiectasis

```{r}
feat = "Bronchiectasis"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cavity

```{r}
feat = "Cavity"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Consolidation

```{r}
feat = "Consolidation"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cyst

```{r}
feat = "Cyst"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Ground Glass

```{r}
feat = "Ground Glass"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Mucoid Impaction

```{r}
feat = "Mucoid Impaction"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Nodule

```{r}
feat = "Nodule"
# Statistic
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Tree in Bud

```{r}
feat = "Tree In Bud"
# Statistics
k=data %>% filter(feature==feat) %>% select(AF:JW) %>% kappam.fleiss(.)
ka= round(k$value,3)
p = format.pval(k$p.value,eps=0.001,digits = 3)
# Plot
data %>% filter(feature==feat) %>%
  select(scan_id,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.
